---
title: "Class 11"
author: "Artie Papandrea"
date: "2026-09-30"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
    code_folding: show
    code_download: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning objectives for Today

- Scrape multiple webpages using `for` loops;

- Scrape multiple webpages using the `purrr::map()` type functions, which would also make you write your own functions in R.

## Extending the Course Bulletin Scrape for multiple departments

 For the sake of the example, let us scrape the following pages:
 [ISA](https://bulletin.miamioh.edu/courses-instruction/isa/) and
 [MKT](https://bulletin.miamioh.edu/courses-instruction/mkt/). From the logic shown in class, you can essentially do that for all fsb departments.
 
 Note that if you are doing it for just a few departments, you can just repeat your code a few times; however, this is bad practice as so we will not do this in class. Software engineers tend to refer to this as : **DRY** (don't repeat yourself)
 
```{r bulletin}
dept_abbr = c('acc', 'bus', 'isa', 'mkt') # extending the example to 4 depts
# line below illustrates how the url can be constructed by pasting) (i.e., no space) the base_url, dept_abbreviation and the forward slash



courses_df = data.frame() # initialize the container
for (dept_name in dept_abbr) {
  cat(rep("-", 25))
  print(dept_name)
  dept_url = paste0("https://bulletin.miamioh.edu/courses-instruction/", dept_name, "/")
  
  # for the titles, I will use the selector gadget and for the desc, I will use the inspector (to show you the alternative CSS selectors for what we did on Mon)
  webpage = rvest::read_html(dept_url)
  
  webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles
  webpage |> 
    rvest::html_elements("#sc_sccoursedescs > div > p.courseblockdesc") |> 
    rvest::html_text2() -> descs
  
  df = data.frame(title = titles, desc = descs)
  df$title[1] |> print() # showing only the first course title
  
  courses_df = rbind(courses_df, df)
  cat(rep("-", 25))
}









```
 

## Re-examining the prior example with the `purrr` package

My preferred approach with the purrr functons is to first create my ownfunction and then use it within the package

```{r}
scrape_mu_bulletin = function(dept_url){
  webpage = rvest::read_html(dept_url)
  
  webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles
  webpage |> 
    rvest::html_elements("#sc_sccoursedescs > div > p.courseblockdesc") |> 
    rvest::html_text2() -> descs
  
  df = data.frame(title = titles, desc = descs)
  
  return(df)
}

test = scrape_mu_bulletin("https://bulletin.miamioh.edu/courses-instruction/bus/")

dept_abbr = c('acc', 'bus', 'isa', 'mkt')
my_urls = paste0("https://bulletin.miamioh.edu/courses-instruction/", # single chr string
                 dept_abbr, # vector of 4 obs
                 "/") # single chr string


# the map function take one or more inputs (depending on the function you are using)
# in this example, we only have 1 input for our function
# sp we used map_() instead of map2_() [2 is for 2 inputs]
#.x = the vector you are iterating over
courses_df_from_purrr = purrr::map_df(.x = my_urls, .f = scrape_mu_bulletin)

head(courses_df_from_purrr)
```

## Scraping Plane Crash Data

We will use `purrr` based on a class vote.

```{r}
year = 2026
#always check the url code in browser before proceeding
plane_url = paste0("https://www.planecrashinfo.com/", year, "/", ".htm") 

webpage = rvest::read_html(plane_url)
#webpage |> rvest::html_element("center > table") |> rvest::html_table()
```














